Refinements for open automata

### 2023-02-27 2021-Refinement/paper/refinementarticleV2.tex
proof with reachability

Let $R$ be the refinement relation relating states of $A_1$ and $A_2$. 
Let us denote with $t^1$ and $t^2$  the elements of $A_1$ and $A_2$ respectively.
Consider any two states $s_{13} = \mpar{s_1,s^1_3}$ and $s_{23} = \mpar{s_2,s^2_3}$ ($s^1_3$ and $s^2_3$  are the same with renaming). We define a relation $R'$ relating states of $s_{13}$ and $s_{23}$ as follows:
\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}}  %\wedge \reach{A_{13}}\mpar{s_{13}}
 \wedge \bigwedge_\subbox{v_3\in V_3}
 v^1_3=v^2_3\wedge s^1_3 = s^2_3\]

@@

Additionally, because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
\begin{align*}
& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} 
%\wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}
\\
\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}}  \land \mpar{\,\,\bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }\\
\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge  \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03}\uplus \sigma_{013} }\\
\implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
\end{align*}
\item Second, we need to prove for any open transition $t_{13}$ in $T_{13}$ originating from $s_{13}$:
\begin{align*}
		&  \OTx{13}{}{13}{13} \in \fOT{s_{13}}
\end{align*}		
there exists an indexed family $t_{23x}$ of OTs originating from $s_{23}$ that simulate it: 
\begin{align*}
		&  \mpar{\OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}
\end{align*}	
\begin{align*}		
		& \text{such that } \mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\
		& R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \wedge\\[12pt]
			 g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{align*}
Recall that by definition of composition and open automata refinement we have: 
\begin{align*}
&V_{13}= V_1\uplus V^1_3 \text{ and }
V_{23}= V_2\uplus V^2_3\\
& H' \subseteq J_3\uplus \mpar{J_1 \cap J_2} \setminus \{k\} = \mpar{J_3\uplus J_1 \setminus \{k\} } \cap \mpar{J_3\uplus J_2 \setminus \{k\}} \\
\end{align*}
First of all, we have by hypothesis $\wrel{A_1}{A_2}{H}$, then for any open transition $t_1$ in $T_1$  originating from $s_1$:
\begin{align*}
\OTx{1}{}{1}{1} \in \fOT{s_1}
\end{align*}
there exists an indexed family of OTs originating from $s_{2}$: 
\begin{align*}
\mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_{2}}}^{x \in X} 
\end{align*}
such that $\forall x \in X, J'_{2x} \cap H = J'_1 \cap H$ and
\begin{multline*}
%\everymath{\displaystyle}
V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R\mpar{s_1, s_{2}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \nwedge\\
			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}}  \qquad \quad (*)
\end{multline*}	
\smallskip

@@

In this case the composition gives: \[g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k} \text{ and }
g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}\]
As $k \in H$ we have   
$\beta_{1k} = \beta_{2xk}$ then we  deduce:
\[g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}\]
The proof of the rest  is based on the following facts: 
\begin{enumerate}
\item  Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transitions $t_3$ and .   By construction of  $t_{13}$ and $t_{23x}$ we have $\alpha_{13}=
\alpha_{1}$ and $\alpha_{23x}=\alpha_{2x}$. So we deduce: 
$\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.
\item By composition we have also: \\ $\beta_{13j}^{j\in J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
and $\beta_{23xj}^{j\in J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
Therefore, we have for all $j\in J'_{13}$ (recall that $J'_{13}=J'_{23}$):  \[\beta_{13j} = \beta_{23xj} \Rightarrow (j\in J'_1 \land \beta_{1j} = \beta_{2xj}) \vee (j\in J_3^{1\prime} \land \beta^1_{3j}= \beta^2_{3j})\]
\item 
Considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: \\
${\displaystyle V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}} \vdash \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$\\
The disjunction with the following hypothesis:\\ $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$  will give:
\begin{align*}
 V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}}\vdash &    \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3 \implies {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\  
\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in    ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
\Rightarrow    V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}
\end{align*}
\end{enumerate}

By the extension of the valuation context mentioned above in the formula $(*)$ and by using the statements resulting from the cases (a), (b) and (c), we get:
\begin{multline*}
V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
R\mpar{s_1, s_{2}} \wedge \mpar{g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}}\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 %\wedge s^1_3=s^2_3
\implies  \hspace{12em}\\
\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in (J'_{23x} \cap H')} \beta_{13j}\! =\! \beta_{23xj}\nwedge\\
			  g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}  \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk} 
%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\end{multline*}	
That can be re-written as follows:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3
\implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge\\
			g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}   
\end{multline*}

@@

\RAB{ I think there is no need to the no blocking condition} Furthermore, by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
Thus, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \cancel{\wedge \reach{A_{13}}\mpar{s_{13}}}
\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
		  \wedge \cancel{\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
\wedge} \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
		\end{array}}   
\end{multline*}

From the two previous formulas, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13} \land \cancel{\reach{A_{13}}\mpar{s_{13}} \land} \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land  \cancel{\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}}		\nwedge\\
			  R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge
 \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
		\end{array}}   
\end{multline*}

@@

These two cases define (depending on how $t_{13}$ is built) the family $t_{23x}$ of OTs we are looking for.
Thus, for both cases we have to prove the following:
\begin{align*}		
		&\mpar{\forall x \in X, J'_{23x} \cap H' =
 J'_{13} \cap H'} \text{ and }\\
		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ & R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge\\[12pt]
			g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{align*}

Recall in this second case, i.e. where only $A_1$ performs a transition $t_{13}$,  $k \notin J'_1$, $\forall x \in X$ we have
\begin{align*}		
J'_{23x} \cap H' & = J'_{2x}  \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
& = \mpar{J'_1\cap H } \text{  since } J'_1 \cap H = J'_{2x} \cap H\\
& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'
\end{align*}

The proof of the rest of the formula follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{13} \Leftrightarrow g_1$ and
$g_{23x}  \Leftrightarrow g_{2x}$.\\

\item \TODO{To check from this point:} Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
\begin{multline*}
V_{13} \uplus V_{23}  \vdash  R\mpar{s_{13}, s_{23}} \nwedge  \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg (\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}) 
\end{multline*}

By hypothesis  the second  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Non-block} we have for all state $s_{13}$ which is reachable, i.e. $ \fvars{t_{13}}\vdash \reach{A_{13}}\mpar{s_{13}}$,  the following:

\begin{multline*}
V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}  \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}
\end{multline*}
From this we can infer:
\begin{multline*}
V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash  \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})  \implies   \neg(\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1})
\end{multline*}

>>>>

Let $R$ be the refinement relation relating states of $A_1$ and $A_2$. 
Let us denote with $t^1$ and $t^2$  the elements of $A_1$ and $A_2$ respectively.
Consider any two states $s_{13} = \mpar{s_1,s^1_3}$ and $s_{23} = \mpar{s_2,s^2_3}$ ($s^1_3$ and $s^2_3$  are the same with renaming). We define a relation $R'$ relating states of $s_{13}$ and $s_{23}$ as follows:
\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}} \land \reach{A_{13}}(s_{13})  %\wedge \reach{A_{13}}\mpar{s_{13}}
 \wedge \bigwedge_\subbox{v_3\in V_3}
 v^1_3=v^2_3\land s^1_3 = s^2_3\]

@@

Additionally, because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
\begin{align*}
& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} 
%\wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}
\\
\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}}  \land \mpar{\,\,\bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }\\
\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge  \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03}\uplus \sigma_{013} }\\
\implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
\end{align*}
The last step comes from the additional fact that  $\reach{A_{13}}(s_{013})$.

\item Second, we need to prove for any open transition $t_{13}$ in $T_{13}$ originating from $s_{13}$:
\begin{align*}
		&  \OTx{13}{}{13}{13} \in \fOT{s_{13}}
\end{align*}		
there exists an indexed family $t_{23x}$ of OTs originating from $s_{23}$ that simulate it: 
\begin{align*}
		&  \mpar{\OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}
\end{align*}	
\begin{align*}		
		& \text{such that } \mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\
		& R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \wedge\\[12pt]
			 g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{align*}

Recall that by definition of composition and open automata refinement we have: 
\begin{align*}
&V_{13}= V_1\uplus V^1_3 \text{ and }
V_{23}= V_2\uplus V^2_3\\
& H' \subseteq J_3\uplus \mpar{J_1 \cap J_2} \setminus \{k\} = \mpar{J_3\uplus J_1 \setminus \{k\} } \cap \mpar{J_3\uplus J_2 \setminus \{k\}} \\
\end{align*}
First of all, we have by hypothesis $\wrel{A_1}{A_2}{H}$, then for any open transition $t_1$ in $T_1$  originating from $s_1$:
\begin{align*}
\OTx{1}{}{1}{1} \in \fOT{s_1}
\end{align*}
there exists an indexed family of OTs originating from $s_{2}$: 
\begin{align*}
\mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_{2}}}^{x \in X} 
\end{align*}
such that $\forall x \in X, J'_{2x} \cap H = J'_1 \cap H$ and
\begin{multline*}
%\everymath{\displaystyle}
V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R\mpar{s_1, s_{2}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \nwedge\\
			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}}  \qquad \quad (*)
\end{multline*}	
\smallskip

@@

In this case the composition gives: \[g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k} \text{ and }
g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}\]
As $k \in H$ we have   
$\beta_{1k} = \beta_{2xk}$ then we  deduce:
\[g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}\]
The proof of the rest  is based on the following facts: 
\begin{enumerate}
\item  By construction of  $t_{13}$ and $t_{23x}$ we have $\alpha_{13}=
\alpha_{1}$ and $\alpha_{23x}=\alpha_{2x}$. So we deduce: 
$\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.
\item By composition we have also: \\ $\beta_{13j}^{j\in J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
and $\beta_{23xj}^{j\in J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
Therefore, we have for all $j\in J'_{13}$ (recall that $J'_{13}=J'_{23}$):  \[\beta_{13j} = \beta_{23xj} \Rightarrow (j\in J'_1 \land \beta_{1j} = \beta_{2xj}) \vee (j\in J_3^{1\prime} \land \beta^1_{3j}= \beta^2_{3j})\]
\item 
Considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: \\
${\displaystyle V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}} \vdash \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$\\
Then we compose by  disjunction with the following hypothesis (part of formula $(*)$).\\ $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$ 
\begin{align*}
 V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}}\vdash &    \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3 \implies {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\  
\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in    ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
\Rightarrow    V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}
\end{align*}
\end{enumerate}

We can extend the valuation context of the variables to cover the variables of the transitions $t_3$ and the variables in $V_3^1$ and $V_3^2$ in the formula $(*)$.  
By   using the statements resulting from the cases (a), (b) and (c), we get:
\begin{multline*}
V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
R\mpar{s_1, s_{2}} \wedge \mpar{g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}}\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 %\wedge s^1_3=s^2_3
\implies  \hspace{12em}\\
\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in (J'_{23x} \cap H')} \beta_{13j}\! =\! \beta_{23xj}\nwedge\\
			  g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}  \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk} 
%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\end{multline*}	
That can be re-written as follows:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3
\implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge\\
			g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}   
\end{multline*}

@@

 Furthermore, by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have, for all $t_{13} \in T_{13}$:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
Thus, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  {\wedge \reach{A_{13}}\mpar{s_{13}}}
\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
		  \wedge {\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
\wedge} \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
		\end{array}}   
\end{multline*}

From the two previous formulas, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13} \land {\reach{A_{13}}\mpar{s_{13}} \land} \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land  {\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}}		\nwedge\\
			  R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge
 \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
		\end{array}}   
\end{multline*}

@@

\TODO{do this case: the following is old text that makes no sense}
Principle:
\TODO{The proof of the rest of the formula follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{13} \Leftrightarrow g_1$ and $g_{23x}  \Leftrightarrow g_{2x}$}
%
%These two cases define (depending on how $t_{13}$ is built) the family $t_{23x}$ of OTs we are looking for.
%Thus, for both cases we have to prove the following:
%\begin{align*}		
%		&\mpar{\forall x \in X, J'_{23x} \cap H' =
% J'_{13} \cap H'} \text{ and }\\
%		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ & R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
%			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge\\[12pt]
%			g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
%		\end{array}} 
%	\end{align*}
%	
%Recall in this second case, i.e. where only $A_1$ performs a transition $t_{13}$,  $k \notin J'_1$, $\forall x \in X$ we have
%\begin{align*}		
%J'_{23x} \cap H' & = J'_{2x}  \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
%& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
%& = \mpar{J'_1\cap H } \text{  since } J'_1 \cap H = J'_{2x} \cap H\\
%& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'
%\end{align*}
%
%The proof of the rest of the formula follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{13} \Leftrightarrow g_1$ and
%$g_{23x}  \Leftrightarrow g_{2x}$.\\

\item Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
\begin{multline*}
V_{13} \uplus V_{23}  \vdash  R\mpar{s_{13}, s_{23}} \nwedge  \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg (\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}) 
\end{multline*}

By hypothesis  the composition  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Non-block} we have for all state $s_{13}$:

\begin{multline*}
V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}  \vdash  \left(\reach{A_{13}(s_{13})} \land \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}\right) \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}
\end{multline*}
From this we can infer:
\begin{multline*}
V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash  \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})  \implies   \neg(\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \lor 
\neg{\reach{A_{13}(s_{13})}}
\end{multline*}
